Thermodynamic fragments in magic state theories

### 2021-02-15 magic_paper.tex
First attampt at fixing code

	Let $\tt$ be the number of elbows of $\lc{\tau}{\sigma}(x)$ and $E \coloneqq \{x_1, \dots, x_\tt\}$ be their locations.

	Then, $\lc{\rho}{\sigma}(x) \geq \lc{\tau}{\sigma}(x)$ for all $x \in [0,1]$ iff $\lc{\rho}{\sigma}(x_{\ii}) \geq \lc{\tau}{\sigma}(x_{\ii})$ for all $\ii =1,\dots,\tt$.
\end{theorem}
A proof is provided in~\cref{app:lc_constraints}.
Any of the $t$ inequalities in the theorem provides a valid contraint leading to some upper distillation bound, and the more one cosiders, the stricter the bound is.

@@

Denote an $n$-copy, $\epsilon$-noisy magic state $\rho$ in the $\sigma$--fragment by
\begin{equation}\label{eq:dist}
    \rho(\epsilon)\too{n} = \left[ (1 - \epsilon) \rho + \epsilon \sigma \right]\too{n},
\end{equation}
and consider the general magic state distillation (MSD) / purification process
\begin{equation}
		\rho(\epsilon)\too{n} \xrightarrow{\E \in \O_\sigma} \rho(\epsilon')\too{\tt},
\end{equation}
where it is converted into a $\tt$-copy, $\epsilon'$-noisy state, such that the number of copies has decreased ($\tt < n$), but the state is less noisy ($\epsilon' < \epsilon$).

The more noisy the initial state is, the more copies needed to reach the target. 
We make this idea precise by defining the \emph{noise level threshold} as
\begin{equation}\label{eq:ethresh}
	\begin{split}
	\epsilon_{\star}(n, \tt, \epsilon', \sigma) \coloneqq &\sup{\{\epsilon:\ \lc{\rho(\epsilon)\too{n}}{\sigma}}(x) \geq \\
	&{\lc{\rho(\epsilon')\too{\tt}}{\sigma}(x),\ x\in[0,1]\}}.
	\end{split}
\end{equation}
The MSD process~(\ref{eq:dist}) is impossible for all $\epsilon > \epsilon_{\star}(n, \tt, \epsilon', \sigma)$.

@@

In general, the Wigner components of an $\NN$-copy state $\rho\too{\NN}$ can be calculated directly from $\W{\rho}$ by convolution of the distribution with itself,
\begin{equation}
	\W{\rho\too{\NN}} = \rm{W}_{\rho}\too{\NN},
\end{equation}
where $\otimes$ can be interpreted as the usual Kroenecker product in the last expression.
Furthermore, single-copy Lorenz curves are simply additive in noise, 
\begin{equation}
\lc{(1-\epsilon)\rho + \epsilon\sigma}{\sigma} = (1-\epsilon)\lc{\rho}{\sigma} + \epsilon\lc{\sigma}{\sigma},
\end{equation}
for any $\sigma, \rho$.
This is not true for higher number of copies.

@@

We would now like to study the constraints coming solely from majorization in the unital fragment. 
We consider the problem of purifying $n$ copies of a noisy strange state $\noisysn$ into a smaller number of copies $\tt$ of a less noisy strange state $\noisys(\epsilon')\too{\tt}$, with $\epsilon' \le \epsilon$ and $\tt \leq n$. 
Since the state $\frac{1}{3} \id$ is free, the interconversion problem is unaffected if we tensor in copies of it. More precisely the associated Lorenz curve in invariant under tensoring in arbitrary many copies of this free state.
This turns out to simplify the Lorenz curve analysis, and so we focus on the process,
\begin{equation}\label{eq:sudist}
	\noisys\too{n} \longrightarrow \noisys(\tt, \epsilon', n - n') \coloneqq  \noisys(\epsilon')\too{\tt} \otimes \left( \frac{1}{3}\id \right)\too{(n-\tt)},
\end{equation}
where all copies $n, \tt, n - \tt$ are even.
Since the initial state can be written in the form $\noisys(n, \epsilon, 0)$, it suffices to construct the Lorenz curve $\lc{\noisys}{\id/3}(x)$ for the generic noisy strange state $\noisys(n, \epsilon ,\tt)$.
This curve is defined at $9^n$ points between $0$ and $1$.
The exact expressions for the coordinates of these points can take $8$ different forms, depending on whether the noise level $\epsilon$ is greater than or less than $\frac{3}{7}$, the parity of the number of copies $n$ is even/odd and the location relative to the curve peak is on the left hand side (LHS -- including the maximum) / right hand side (RHS).
The full details are provided in~\cref{app:lcsu_technical}.

Here we focus on the case of Lorenz curves of even copies $n, \tt$ and low noise levels ($\epsilon \leq 3/7$).
The part of the curve on the LHS of its peak is constructed by the positive components of the state Wigner distribution that take values $w_\ii$, with associated multiplicities $\mlt_\ii$,
\begin{align}
	w_\ii &= \left( \frac{1}{6} - \frac{1}{18}\epsilon \right)^{2\ii}\left( -\frac{1}{3} + \frac{4}{9}\epsilon \right)^{n-2\ii}, \\
	m_\ii &= 8^{2\ii}\binom{n}{2\ii},
\end{align}
where $i=0,\dots,\frac{n}{2}$.
From this, it is readily seen that $\lc{\rho}{\id/3}(x)$ has elbows on the LHS of its peak located at points $x=x_\ii$, where
\begin{equation}
	x_\ii = \Phi_+ \left( 2\ii; n , \frac{8}{9} \right),
\end{equation}
with $\ii = 0,1, \dots , n$ and where $\Phi_+(i,n,p)$ is an even-power cumulant distribution function given by
\begin{equation}
	\Phi_+(2\ii; n, p) \coloneqq \sum_{\dummy=0}^{\ii} \binom{n}{2\dummy} p ^{2\dummy} (1-p)^{n-2\dummy}.
\end{equation}
We provide technical details on the function $\Phi_+$ in the appendices.

@@

\iffalse
The coordinates of any point on the Lorenz curve LHS can be expressed as convex sums of the neighbouring elbows,
\begin{align}
    x_{\ii\jj\kk} &= \left( 1-p_{\ii\jj\kk}\right) x_{\ii-1} + p_{\ii\jj\kk} x_{\ii} \label{eq:lcsu_xcoord}\\
    L_{\ii\jj\kk} &= \left( 1-p_{\ii\jj\kk} \right) L_{\ii-1} + p_{\ii\jj\kk} L_{\ii}, \label{eq:lcsu_lcoord}
\end{align}
where we use a three-index parametrisation for the coordinates, with $\ii$ the index of the elbow that follows, $\jj = 1,\dots,\mlt_\ii$ and $\kk=1,\dots,9^{2(n-\tt)}$.
Therefore, for the initial state $\noisys\too{2n}$ we have
\begin{equation}
	p_{\ii\jj\kk} = \frac{\jj}{8^{2\ii}\binom{2n}{2\ii}},
\end{equation}
with $\ii=0,\dots,n,\ \jj(\ii) = 1,\dots,8^{2\ii}\binom{2n}{2\ii}$ and $\kk = 1$.
For the target state $\noisys(\epsilon')\too{2\tt} \otimes \left( \frac{1}{3}\id \right)\too{2(n-\tt)}$,
\begin{equation}
	p'_{\ii'\jj'\kk'} = \frac{\kk' + (\jj'-1)9^{2(n-\tt)}}{9^{2(n-\tt)} 8^{2\ii'}\binom{2\tt}{2\ii'}}
\end{equation}
with $\ii'=0,\dots,\tt,\ \jj'(\ii') = 1,\dots,8^{2\ii'}\binom{\tt}{2\ii'}$ and $\kk' = 1,\dots,9^{2(n-\tt)}$.
\fi

Lorenz curve comparison provides $9^n$ necessary constraints for the process~\cref{eq:sudist}.
\cref{thm:elbows} shows that they can be reduced to $\tt$ independent constraints.
However, in principle we can pick any location $x_\star \in [0,1]$ at which the Lorenz curves are defined and we then get a necessary distillation constraint, 
\begin{equation}
	\lc{\noisys(n, \epsilon, 0)}{\frac{\id}{3}}(x_\star) \geq \lc{\noisys(\tt, \epsilon', n-\tt)}{\frac{\id}{3}}(x_\star).
\end{equation}

@@

The first elbow of the target state is located at $x'_0 = \frac{1}{9^{\tt}} > x_\star$, so in order to find the target state Lorenz curve coordinate $L'_\star$ at location $x_\star$, we can interpolate between the origin and the first target state elbow, 
\begin{equation}\label{eq:constraint_deriv}
	\begin{split}
	L'_\star &= \frac{x_\star}{x'_0}L'_0 = \frac{1}{9^{n-\tt}}\left( \frac{5}{3} - \frac{8}{9}\epsilon'\ \right)^{\tt}\Phi_+\left(0;\tt,\frac{12-4\epsilon'}{15-8\epsilon'}\right) \\
	&= \frac{(3-4\epsilon')^{\tt}}{9^{n}}.
	\end{split}
\end{equation}
The process in~\cref{eq:sudist} is therefore possible only if $L_\star \geq L'_\star$ or equivalently,
\begin{align}
	\frac{n}{n'} &\geq \frac{\ln{(3-4\epsilon')}}{\ln{(3-4\epsilon)}}, \text{ or}\\
	\epsilon &\leq \frac{3}{4} - \frac{1}{4}(3-4\epsilon')^{\frac{\tt}{n}}.
\end{align}
As an example, the process with $(n, \tt) = (12, 4)$ and $\epsilon' = 0.05$ yields $\epsilon \leq 0.398$.
Numerical comparison of the curves with varying $\epsilon$ suggests that we require $\epsilon \leq 0.373$ for the process to be possible.

@@

Given a state $\rho$ and a complete set of component-multiplicity pairs describing its Wigner distribution $\W{\rho}$, we now provide a method of computing the components (and multiplicities) of the $n$-copy distribution $\W{\rho}\too{n}$.
\begin{lemma}\label{lem:ncopycomponents}
	Let $W$ be a $d$-dimensional distribution defined by a complete set of component-multiplicity pairs $\{(w_i, m_i)\}_{i=1,\dots,D}$ with $D \leq d$ and consider the distribution $W\too{n}$ obtained by taking the Kronecker product $W \otimes \dots \otimes W$ between $n$ copies of $W$.

@@

	Then, $W\too{n}$ admits a complete set of component-multiplicity pairs $\{(W_{\bmk}, M_{\bmk})\}_{\bmk \in C_D^n}$, where
\begin{align}
	M_{\bmk} &= \frac{n!}{k_1!\dots k_D!} \prod\limits_{i=1}^D {m_i}^{k_i}, \label{eq:M}\\
	W_{\bmk} &= \prod\limits_{i=1}^D {w_i}^{k_i}. \label{eq:W}
\end{align}
\end{lemma}
\begin{proof}
	We proceed by induction.

@@

	Assume that $\{(W_{\bmk}, M_{\bmk})\}_{\bmk \in C_D^n}$ as given in~\cref{eq:M,eq:W} is a complete set of component-multiplicity pairs for the $n$-copy distribution $W\too{n}$.
	By construction, the distribution $W\too{(n+1)} = W\too{n} \otimes W$ is multiplicative, so it admits the complete set of component multiplicity pairs
\begin{equation}
	\{(W_{\bmk} w_i, M_{\bmk} m_i)\},\ \bmk \in C_D^n \text{ and } i=1,\dots,D.
\end{equation}

	Consider the component sum of the distribution $W\too{(n+1)}$,
\begin{align*}
	&\sum_{\bmk \in C_D^n}\sum_{i=1}^D M_{\bmk} m_i W_{\bmk} w_i = \sum_{\bmk \in C_D^n} M_{\bmk}W_{\bmk} \sum_{i=1}^D m_i w_i =\\
	&\sum_{\bmk \in C_D^n} \frac{n!}{k_1!\dots k_D!} \prod\limits_{i=1}^D {m_i}^{k_i}{w_i}^{k_i} \sum_{i=1}^D m_i w_i =\\
	&\left( \sum_{i=1}^D m_i w_i \right)^n \left( \sum_{i=1}^D m_i w_i \right) = \left( \sum_{i=1}^D m_i w_i \right)^{n+1} =\\
	&\sum_{\bmq \in C_D^{n+1}} M_{\bmq}W_{\bmq},
\end{align*}
where in the last expression, vectors $\bmq = (q_1, \dots, q_D)$ have non-negative integer components that sum to $(n+1)$ and 
\begin{align*}
	M_{\bmq} &= \frac{(n+1)!}{q_1!\dots q_D!} \prod\limits_{i=1}^D {m_i}^{q_i},\\
	W_{\bmq} &= \prod\limits_{i=1}^D {w_i}^{q_i}.
\end{align*}
We have used the multinomial theorem to proceed between lines 2-3 and lines 3-4 of the derivation.

We have achieved a regrouping of the distribution components.
Every component $W_{\bmq}$ is of the form $W_{\bmk} w_i$ with $q_i = k_i + 1$ and $q_j = k_j$ for $j\neq i$ and 
\begin{align*}
	\sum_{\bmq \in C_D^{n+1}}  \hspace{-6pt} M_{\bmq} =  \hspace{-10pt} \sum_{\bmq \in C_D^{n+1}} \frac{(n+1)!}{q_1!\dots q_D!} \prod\limits_{i=1}^D {m_i}^{q_i} = 
	\left( \sum_{i=1}^D m_i \right)^{n+1} \hspace{-10pt} = d^{n+1},
\end{align*}
which is the dimension of $W\too{(n+1)}$.

Therefore, $\{ (W_{\bmq}, M_{\bmq}) \}_{\bmq \in C_D^{n+1}}$ is a complete set of component-multiplicity pairs for $W\too{n}$, completing the proof.
\end{proof}

\ddd{Note the following is relevant: you might have $W_{\bmq} = W_{\bmq'}$ for two different $\bmq$, $\bmq'$. This would make a difference to our calculations for the first elbow. Check this doesn't occur. (If it does, our analysis is still correct, but it simply could be improved).}

@@

We are now in a position to consider the Strange state distillation process
\begin{equation}\label{eq:msd_thermal}
		\noisys(\epsilon)\too{n} \xrightarrow{\E \in \O_{\gamma_\beta}} \noisys(\epsilon')\too{\tt} \otimes \gamma_\beta\too{(n-\tt)},
\end{equation}
where we are allowed to tensor in copies of the thermal state $\gamma_\beta$, since it is free in fragment $\O_{\gamma_\beta}$.

Our aim is to obtain a distillation bound for~\cref{eq:msd_thermal} which depends on variables $n, \tt, \epsilon, \epsilon'$ as well as $\beta$.
In the analysis that follows, we drop obvious variable dependencies for clarity.

@@

In order to construct the $n$-copy Lorenz curve of a Strange state in a thermal fragment we need to sort the components of the $n$-copy Gibbs-rescaled distribution, $w(\noisys | \gamma)_{ijk}$ in decreasing order.
In particular, to find the coordinates of the first elbow $(x_0, L_0)$, we need to evaluate the greatest component,
\begin{align}
	&\bmw(\noisys | \gamma)_{\rm{max}} \coloneqq \label{eq:max_slope}\\
	&(3\Z)^{n} \max\limits_{i,j,k}\Big\{ (-v)^{n-\alpha} u^{\alpha} e^{\beta (n-\alpha)E_0} e^{\beta ( i E_0 + j E_1 + k E_2 )} \Big\}, \nonumber
\end{align}
where $0 \leq i,j,k \leq n$ and $\alpha \coloneqq i+j+k \leq n$.
Notice that for $0 \leq \epsilon \leq 3/7$, we have $v \geq u$. We assume that $n$ is even, ans so we then need the sum $\alpha = i+j+k$ to be even, so that the expression is positive.

>>>>

	Let $n'$ be the number of elbows of $\lc{\tau}{\sigma}(x)$ and $E \coloneqq \{x_1, \dots, x_n'\}$ be their locations.

	Then, $\lc{\rho}{\sigma}(x) \geq \lc{\tau}{\sigma}(x)$ for all $x \in [0,1]$ iff $\lc{\rho}{\sigma}(x_{\ii}) \geq \lc{\tau}{\sigma}(x_{\ii})$ for all $\ii =1,\dots,n'$.
\end{theorem}
A proof is provided in~\cref{app:lc_constraints}.
Any of the $t$ inequalities in the theorem provides a valid contraint leading to some upper distillation bound, and the more one cosiders, the stricter the bound is.

@@

Denote an $n$-copy, $\epsilon$-noisy magic state $\rho$ in the $\sigma$--fragment by
\begin{equation}\label{eq:dist}
    \rho(\epsilon)^{\otimes n} = \left[ (1 - \epsilon) \rho + \epsilon \sigma \right]^{\otimes n},
\end{equation}
and consider the general magic state distillation (MSD) / purification process
\begin{equation}
		\rho(\epsilon)^{\otimes n} \xrightarrow{\E \in \O_\sigma} \rho(\epsilon')^{\otimes n'},
\end{equation}
where it is converted into a $n'$-copy, $\epsilon'$-noisy state, such that the number of copies has decreased ($n' < n$), but the state is less noisy ($\epsilon' < \epsilon$).

The more noisy the initial state is, the more copies needed to reach the target. 
We make this idea precise by defining the \emph{noise level threshold} as
\begin{equation}\label{eq:ethresh}
	\begin{split}
	\epsilon_{\star}(n, n', \epsilon', \sigma) \coloneqq &\sup{\{\epsilon:\ \lc{\rho(\epsilon)^{\otimes n}}{\sigma}}(x) \geq \\
	&{\lc{\rho(\epsilon')^{\otimes n'}}{\sigma}(x),\ x\in[0,1]\}}.
	\end{split}
\end{equation}
The MSD process~(\ref{eq:dist}) is impossible for all $\epsilon > \epsilon_{\star}(n, n', \epsilon', \sigma)$.

@@

In general, the Wigner components of an $\NN$-copy state $\rho^{\otimes \NN}$ can be calculated directly from $\W{\rho}$ by convolution of the distribution with itself,
\begin{equation}
	\W{\rho^{\otimes \NN}} = \rm{W}_{\rho}^{\otimes \NN},
\end{equation}
where $\otimes$ can be interpreted as the usual Kroenecker product in the last expression.
Furthermore, single-copy Lorenz curves are simply additive in noise, 
\begin{equation}
\lc{(1-\epsilon)\rho + \epsilon\sigma}{\sigma} = (1-\epsilon)\lc{\rho}{\sigma} + \epsilon\lc{\sigma}{\sigma},
\end{equation}
for any $\sigma, \rho$.
This is not true for higher number of copies.

@@

We would now like to study the constraints coming solely from majorization in the unital fragment. 
We consider the problem of purifying $n$ copies of a noisy strange state $\noisysn$ into a smaller number of copies $n'$ of a less noisy strange state $\noisys(\epsilon')^{\otimes n'}$, with $\epsilon' \le \epsilon$ and $n' \leq n$. 
Since the state $\frac{1}{3} \id$ is free, the interconversion problem is unaffected if we tensor in copies of it. More precisely the associated Lorenz curve in invariant under tensoring in arbitrary many copies of this free state.
This turns out to simplify the Lorenz curve analysis, and so we focus on the process,
\begin{equation}\label{eq:sudist}
	\noisys^{\otimes n} \longrightarrow \noisys(n', \epsilon', n - n') \coloneqq  \noisys(\epsilon')^{\otimes n'} \otimes \left( \frac{1}{3}\id \right)^{\otimes (n-n')},
\end{equation}
where all copies $n, n', n - n'$ are even.
Since the initial state can be written in the form $\noisys(n, \epsilon, 0)$, it suffices to construct the Lorenz curve $\lc{\noisys}{\id/3}(x)$ for the generic noisy strange state $\noisys(n, \epsilon ,n')$.
This curve is defined at $9^n$ points between $0$ and $1$.
The exact expressions for the coordinates of these points can take $8$ different forms, depending on whether the noise level $\epsilon$ is greater than or less than $\frac{3}{7}$, the parity of the number of copies $n$ is even/odd and the location relative to the curve peak is on the left hand side (LHS -- including the maximum) / right hand side (RHS).
The full details are provided in~\cref{app:lcsu_technical}.

Here we focus on the case of Lorenz curves of even copies $n, n'$ and low noise levels ($\epsilon \leq 3/7$).
The part of the curve on the LHS of its peak is constructed by the positive components of the state Wigner distribution that take values $w_\ii$, with associated multiplicities $\mlt_\ii$,
\begin{align}
	w_\ii &= \left( \frac{1}{6} - \frac{1}{18}\epsilon \right)^{2\ii}\left( -\frac{1}{3} + \frac{4}{9}\epsilon \right)^{n-2\ii}, \\
	m_\ii &= 8^{2\ii}\binom{n}{2\ii},
\end{align}
where $i=0,\dots,\frac{n}{2}$.
From this, it is readily seen that $\lc{\rho}{\id/3}(x)$ has elbows on the LHS of its peak located at points $x=x_\ii$, where
\begin{equation}
	x_\ii = \Phi_+ \left( 2\ii; n , \frac{8}{9} \right),
\end{equation}
with $\ii = 0,1, \dots , n$ and where $\Phi_+(i,n,p)$ is an even-power cumulant distribution function given by
\begin{equation}
	\Phi_+(2\ii; n, p) \coloneqq \sum_{\dummy=0}^{\ii} \binom{n}{2\dummy} p ^{2\dummy} (1-p)^{n-2\dummy}.
\end{equation}
We provide technical details on the function $\Phi_+$ in the appendices.

@@

\iffalse
The coordinates of any point on the Lorenz curve LHS can be expressed as convex sums of the neighbouring elbows,
\begin{align}
    x_{\ii\jj\kk} &= \left( 1-p_{\ii\jj\kk}\right) x_{\ii-1} + p_{\ii\jj\kk} x_{\ii} \label{eq:lcsu_xcoord}\\
    L_{\ii\jj\kk} &= \left( 1-p_{\ii\jj\kk} \right) L_{\ii-1} + p_{\ii\jj\kk} L_{\ii}, \label{eq:lcsu_lcoord}
\end{align}
where we use a three-index parametrisation for the coordinates, with $\ii$ the index of the elbow that follows, $\jj = 1,\dots,\mlt_\ii$ and $\kk=1,\dots,9^{2(n-n')}$.
Therefore, for the initial state $\noisys^{\otimes 2n}$ we have
\begin{equation}
	p_{\ii\jj\kk} = \frac{\jj}{8^{2\ii}\binom{2n}{2\ii}},
\end{equation}
with $\ii=0,\dots,n,\ \jj(\ii) = 1,\dots,8^{2\ii}\binom{2n}{2\ii}$ and $\kk = 1$.
For the target state $\noisys(\epsilon')^{\otimes 2n'} \otimes \left( \frac{1}{3}\id \right)^{\otimes 2(n-n')}$,
\begin{equation}
	p'_{\ii'\jj'\kk'} = \frac{\kk' + (\jj'-1)9^{2(n-n')}}{9^{2(n-n')} 8^{2\ii'}\binom{2n'}{2\ii'}}
\end{equation}
with $\ii'=0,\dots,n',\ \jj'(\ii') = 1,\dots,8^{2\ii'}\binom{n'}{2\ii'}$ and $\kk' = 1,\dots,9^{2(n-n')}$.
\fi

Lorenz curve comparison provides $9^n$ necessary constraints for the process~\cref{eq:sudist}.
\cref{thm:elbows} shows that they can be reduced to $n'$ independent constraints.
However, in principle we can pick any location $x_\star \in [0,1]$ at which the Lorenz curves are defined and we then get a necessary distillation constraint, 
\begin{equation}
	\lc{\noisys(n, \epsilon, 0)}{\frac{\id}{3}}(x_\star) \geq \lc{\noisys(n', \epsilon', n-n')}{\frac{\id}{3}}(x_\star).
\end{equation}

@@

The first elbow of the target state is located at $x'_0 = \frac{1}{9^{n'}} > x_\star$, so in order to find the target state Lorenz curve coordinate $L'_\star$ at location $x_\star$, we can interpolate between the origin and the first target state elbow, 
\begin{equation}\label{eq:constraint_deriv}
	\begin{split}
	L'_\star &= \frac{x_\star}{x'_0}L'_0 = \frac{1}{9^{n-n'}}\left( \frac{5}{3} - \frac{8}{9}\epsilon'\ \right)^{n'}\Phi_+\left(0;n',\frac{12-4\epsilon'}{15-8\epsilon'}\right) \\
	&= \frac{(3-4\epsilon')^{n'}}{9^{n}}.
	\end{split}
\end{equation}
The process in~\cref{eq:sudist} is therefore possible only if $L_\star \geq L'_\star$ or equivalently,
\begin{align}
	\frac{n}{n'} &\geq \frac{\ln{(3-4\epsilon')}}{\ln{(3-4\epsilon)}}, \text{ or}\\
	\epsilon &\leq \frac{3}{4} - \frac{1}{4}(3-4\epsilon')^{\frac{n'}{n}}.
\end{align}
As an example, the process with $(n, n') = (12, 4)$ and $\epsilon' = 0.05$ yields $\epsilon \leq 0.398$.
Numerical comparison of the curves with varying $\epsilon$ suggests that we require $\epsilon \leq 0.373$ for the process to be possible.

@@

Given a state $\rho$ and a complete set of component-multiplicity pairs describing its Wigner distribution $\W{\rho}$, we now provide a method of computing the components (and multiplicities) of the $n$-copy distribution $\W{\rho}^{\otimes n}$.
\begin{lemma}\label{lem:ncopycomponents}
	Let $W$ be a $d$-dimensional distribution defined by a complete set of component-multiplicity pairs $\{(w_i, m_i)\}_{i=1,\dots,D}$ with $D \leq d$ and consider the distribution $W^{\otimes n}$ obtained by taking the Kronecker product $W \otimes \dots \otimes W$ between $n$ copies of $W$.

@@

	Then, $W^{\otimes n}$ admits a complete set of component-multiplicity pairs $\{(W_{\bmk}, M_{\bmk})\}_{\bmk \in C_D^n}$, where
\begin{align}
	M_{\bmk} &= \frac{n!}{k_1!\dots k_D!} \prod\limits_{i=1}^D {m_i}^{k_i}, \label{eq:M}\\
	W_{\bmk} &= \prod\limits_{i=1}^D {w_i}^{k_i}. \label{eq:W}
\end{align}
\end{lemma}
\begin{proof}
	We proceed by induction.

@@

	Assume that $\{(W_{\bmk}, M_{\bmk})\}_{\bmk \in C_D^n}$ as given in~\cref{eq:M,eq:W} is a complete set of component-multiplicity pairs for the $n$-copy distribution $W^{\otimes n}$.
	By construction, the distribution $W^{\otimes (n+1)} = W^{\otimes n} \otimes W$ is multiplicative, so it admits the complete set of component multiplicity pairs
\begin{equation}
	\{(W_{\bmk} w_i, M_{\bmk} m_i)\},\ \bmk \in C_D^n \text{ and } i=1,\dots,D.
\end{equation}

	Consider the component sum of the distribution $W^{\otimes (n+1)}$,
\begin{align*}
	&\sum_{\bmk \in C_D^n}\sum_{i=1}^D M_{\bmk} m_i W_{\bmk} w_i = \sum_{\bmk \in C_D^n} M_{\bmk}W_{\bmk} \sum_{i=1}^D m_i w_i =\\
	&\sum_{\bmk \in C_D^n} \frac{n!}{k_1!\dots k_D!} \prod\limits_{i=1}^D {m_i}^{k_i}{w_i}^{k_i} \sum_{i=1}^D m_i w_i =\\
	&\left( \sum_{i=1}^D m_i w_i \right)^n \left( \sum_{i=1}^D m_i w_i \right) = \left( \sum_{i=1}^D m_i w_i \right)^{n+1} =\\
	&\sum_{\bmq \in C_D^{n+1}} M_{\bmq}W_{\bmq},
\end{align*}
where in the last expression, vectors $\bmq = (q_1, \dots, q_D)$ have non-negative integer components that sum to $(n+1)$ and 
\begin{align*}
	M_{\bmq} &= \frac{(n+1)!}{q_1!\dots q_D!} \prod\limits_{i=1}^D {m_i}^{q_i},\\
	W_{\bmq} &= \prod\limits_{i=1}^D {w_i}^{q_i}.
\end{align*}
We have used the multinomial theorem to proceed between lines 2-3 and lines 3-4 of the derivation.

We have achieved a regrouping of the distribution components.
Every component $W_{\bmq}$ is of the form $W_{\bmk} w_i$ with $q_i = k_i + 1$ and $q_j = k_j$ for $j\neq i$ and 
\begin{align*}
	\sum_{\bmq \in C_D^{n+1}}  \hspace{-6pt} M_{\bmq} =  \hspace{-10pt} \sum_{\bmq \in C_D^{n+1}} \frac{(n+1)!}{q_1!\dots q_D!} \prod\limits_{i=1}^D {m_i}^{q_i} = 
	\left( \sum_{i=1}^D m_i \right)^{n+1} \hspace{-10pt} = d^{n+1},
\end{align*}
which is the dimension of $W^{\otimes (n+1)}$.

Therefore, $\{ (W_{\bmq}, M_{\bmq}) \}_{\bmq \in C_D^{n+1}}$ is a complete set of component-multiplicity pairs for $W^{\otimes n}$, completing the proof.
\end{proof}

\ddd{Note the following is relevant: you might have $W_{\bmq} = W_{\bmq'}$ for two different $\bmq$, $\bmq'$. This would make a difference to our calculations for the first elbow. Check this doesn't occur. (If it does, our analysis is still correct, but it simply could be improved).}
\nick{This is in general true, will check if in our case it makes a difference}

@@

We are now in a position to consider the Strange state distillation process
\begin{equation}\label{eq:msd_thermal}
		\noisys(\epsilon)^{\otimes n} \xrightarrow{\E \in \O_{\gamma_\beta}} \noisys(\epsilon')^{\otimes n'} \otimes \gamma_\beta^{\otimes (n-n')},
\end{equation}
where we are allowed to tensor in copies of the thermal state $\gamma_\beta$, since it is free in fragment $\O_{\gamma_\beta}$.

Our aim is to obtain a distillation bound for~\cref{eq:msd_thermal} which depends on variables $n, n', \epsilon, \epsilon'$ as well as $\beta$.
In the analysis that follows, we drop obvious variable dependencies for clarity.

@@

In order to construct the $n$-copy Lorenz curve of a Strange state in a thermal fragment we need to sort the components of the $n$-copy Gibbs-rescaled distribution, $w(\noisys | \gamma)_{ijk}$ in decreasing order.
In particular, to find the coordinates of the first elbow $(x_0, L_0)$, we need to evaluate the greatest component,
\begin{align}
	&\bmw(\noisys | \gamma)_{\rm{max}} \coloneqq \label{eq:max_slope}\\
	&(3\Z)^{n} \max\limits_{i,j,k}\Big\{ (-v)^{n-\alpha} u^{\alpha} e^{\beta (n-\alpha)E_0} e^{\beta ( i E_0 + j E_1 + k E_2 )} \Big\}, \nonumber
\end{align}
where $0 \leq i,j,k \leq n$ and $\alpha \coloneqq i+j+k \leq n$.
Notice that for $0 \leq \epsilon \leq 3/7$, we have $v \geq u$. 
We assume that $n$ is even, so we then need the sum $\alpha = i+j+k$ to be even, so that the expression is positive.

Given an even value $\alpha$ for the sum, the term $v^{n-\alpha} u^{\alpha} e^{-\beta (n-\alpha)E_0}$ is fixed, so the expression is maximised by setting the coefficient of the highest energy $E_{\rm{max}}$ equal to $\alpha$.
Hence, we have
\begin{align}
	&\bmw(\noisys | \gamma)_{\rm{max}} = \nonumber\\
	&(3\Z)^{n} \max\limits_{\substack{\alpha = 0,2, \\ \dots,n-2,n}}{\Big\{ v^{n-\alpha} u^{\alpha} e^{\beta (n-\alpha)E_0} e^{\beta \alpha E_{\rm{max}}} \Big\}} =  \nonumber\\
	&(3\Z)^{n} v^n e^{n\beta E_0}\max\limits_{\substack{\alpha = 0,2, \\ \dots,n-2,n}}{\Big\{ \left( \frac{u}{v} e^{\beta (E_{\rm{max}} - E_0)} \right)^{\alpha} \Big\}}
\end{align}
If the expression $\frac{u}{v} e^{\beta (E_{\rm{max}} - E_0)}$ is less than $1$ then the maximum occurs at $\alpha=0$, and otherwise the maximum occurs at $\alpha = n$.
The threshold value of $1$ is achieved for this term when the noise level $\epsilon$ is equal to
\begin{equation}
	\epsilon_{\star}(\beta) := 3 - \dfrac{18}{8-e^{(E_{\rm{max}} - E_0)\beta}}.
	%\beta \leq \frac{1}{E_{\rm{max}} - E_0}\ln{\left( 8-\frac{18}{3-\epsilon} \right)}
\end{equation}
For the case $E_{\rm{max}} = E_0$ this threshold is constant in temperature and given by Since $ E_{\rm max} - E_0 \ge 0$ the threshold $\epsilon_{\star}$ is a decreasing function of $\beta$, and it achieves its maximum value $3/7$ for $(E_{\rm{max}} - E_0)\beta = 0$, and a value equal to $0$ for
\begin{equation}
	\beta_{\star} \coloneqq \frac{1}{E_{\rm{max}} - E_0} \ln2.
\end{equation}
For $\beta > \beta_{\star}$, $\epsilon_{\star}$ is negative, meaning that the noise level $\epsilon$ will always be higher than the threshold.
We highlight that the threshold becomes $0$ when the difference between the maximum energy level and the level associated with the state negativity is equal to the energy extracted from a single particle Szilard's engine,
\begin{equation}
	E_{\rm{max}} - E_0 = kT_{\star} \ln2.
\end{equation}

The maximum value of the Gibbs-rescaled distribution finally is
\begin{equation}
\bmw(\noisys | \gamma)_{\rm{max}} =
	\begin{cases}
		(3\Z)^{n} v^n e^{n\beta E_0}, &\epsilon \leq \epsilon_{\star},\ \hspace{30pt}\rm{(C1)}	\\
		(3\Z)^{n} u^n e^{n\beta E_{\rm{max}}}, &\epsilon > \epsilon_{\star}.\ \hspace{32pt}\rm{(C2)} 
	\end{cases}
\end{equation}
Case $\rm{(C1)}$ corresponds to $(i,j,k) = (0,0,0)$, while case $\rm{(C2)}$ corresponds to the  the conditions 
\begin{equation}
	(i,j,k) = 
	\begin{cases}
	(0,n,0), &\text{if } E_{\rm{max}} = E_1, \\
	(0,0,n), &\text{if } E_{\rm{max}} = E_2.
	\end{cases}
\end{equation}
Note that if $E_{\rm{max}} = E_0$, we get $\epsilon_{\star} = 3/7$ and $\rm{(C1)}$ holds for all $\epsilon$ and $\beta$.
Assuming $E_{\rm{max}} > E_0$, we get the cases:
\begin{itemize}
	\item $\beta = 0$. Then, $\epsilon_{\star} = 3/7$ and $\rm{(C1)}$ holds for all noise levels $\epsilon$.
	This is the unital fragment.
	\item $0 < \beta < \beta_{\star}$. Then, $0 < \epsilon_{\star} < 3/7$ and $\rm{(C1)}$ holds for $\epsilon \leq \epsilon_{\star}$, while $\rm{(C2)}$ holds for $\epsilon \geq \epsilon_{\star}$.
	\item $\beta \geq \beta_{\star}$. Then, $ \epsilon_{\star} \leq 0$ and $\rm{(C2)}$ holds for all $\epsilon$.
\end{itemize}
